\propertitle

### 2020-03-17 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T02:31:16+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

In our calculations, however, we are using a zeroth-order Laplace
approximation for calculating the evidence in \sect~4. A first-order
approximation (containing the width of the distribution, influenced by the
typical-set volume above) would correct for the model's power
\citep[\sect~2.2]{mackay1992}. We believe that the correction would
nevertheless be the same in the calculations based on the larger
population, \eqns~(11), and on the sample, \eqns~(12). Hence the difference
in the two approaches -- our main message -- should persist. But it would
be better to check this.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T02:34:29+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

In our calculations of the evidence in \sect~4, however, we are using a
zeroth-order Laplace approximation. A first-order approximation (containing
the width of the distribution, influenced by the typical-set volume above)
would correct for the model's power \citep[\sect~2.2]{mackay1992}. We
believe that the correction would nevertheless be the same in the
calculations based on the larger population, \eqns~(11), and on the sample,
\eqns~(12). Hence the difference in the two approaches -- our main message
-- should persist. But it would be better to check this.
